\cvsection{Experience}
\begin{cventries}
\cventry{Software Architect}{Prodrive Technologies}{Eindhoven}{01.2019 --- now}{
DWorking as part of the team responsible for creating and transferring to China an internal system architecture for end line product used in high volume production. 
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Design architecture of the functional test}
	\item{Conversion the test concept of the PCB, and end line product}
	\item{Performance test qualification, and optimization of the test structure}
	\item{Investigating and analyzing of technical failure root-cause}
\end{itemize}
\textbf{Used technologies}: C++, Python, CI/CD, Jenkins, Cadence.
}


\cventry{{Software Engineer}{Prodrive Technologies}{Eindhoven}{12.2016 --- 12.2018}{
Working in the development and maintenance team in high volume production industry for various clients. Development software of production test for end line products.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Software analysis and development internal solution}
	\item{Design system and software requirements according to specification}
	\item{Create and maintain software design, and associated documentation}
	\item{Integrate software in devices and perform unit and integration testing}
	\item{Developed test and measurement code to be used in production}
	\item{Scrum work environment}
\end{itemize}
\textbf{Used technologies}: JavaScript, HTML5, CSS3, Jira, Python, C++, Jenkins, Git. 
}

\cventry{Intern}{Prodrive Technologies}{Eindhoven}{09.2016 --- 11.2016}{
Interns at Prodrive Technology are an important asset to the team. They welcome interns from different backgrounds. The internship offers me a great way of learning more in my field within the professional context.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Getting familiar with embedded systems devices}
	\item{Assistance in the testing and calibration of the devices}
	\item{Gain knowledge in testing to determine foundation strength prior to construction}
\end{itemize}
}

\end{cventries}
